---
title: "March presentations"
output:
  html_document:
    toc: no
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
library(googlesheets4); library(dplyr)
library(kableExtra); library(lubridate)

options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 

raw <- read_sheet("https://docs.google.com/spreadsheets/d/1MJG0lwuE9f03LXEtaH53j-uJGHwAsAO1ckP_jDAm0gY") %>%
        mutate(dt = date(Date), 
               Name = paste(Name, sprintf("[%s](mailto:%s)", Email, Email)), 
               Affiliation = ifelse(!is.na(webpage), sprintf("[%s](%s)", Affiliation, webpage), Affiliation)) %>% 
        select(-Date, -`Confirmed?`, -Email, -webpage) %>%
        relocate(c(Time,Name), .before=1)


wk1 <- filter(raw, dt=="2021-03-05") %>% arrange(Time)
wk2 <- filter(raw, dt=="2021-03-12") %>% arrange(Time)
wk3 <- filter(raw, dt=="2021-03-19") %>% arrange(Time)

```

> The CSU Math Council Colloquia (MC$^2$) series provides CSU faculty in mathematics, statistics, and mathematics education with the opportunity to network and share best practices in any topics related to university level mathematics and statistics education.

----

# Sustaining Quality Online Learning Through the Pandemic (and Beyond): Sharing Successes with Active Student Engagement.

## Abstract
Regardless of your experience teaching active student-centered classes, the shift to teaching active student-centered online classes during a global pandemic has presented new kinds of challenges for us all. Moreover, the flexibility afforded by online learning will likely lead to more demand for quality online instruction, so instructors will need the relevant skills in their toolkits even after our return to a new normal. Through a series of three interactive sessions we will explore strategies for responding to these challenges and supporting our students’ online learning through this troubling time and beyond.


Hosts: 

* **Julia Olkin**, Professor; Mathematics Department; California State University, East Bay (julia.olkin@csueastbay.edu)

----



## `r format(wk1$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk1$Zoom)[1]`)[[Slides]](`r na.omit(wk1$recording)[1]`) 

```{r, wk1}
wk1 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

## `r format(wk2$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk2$Zoom)[1]`)[[Recording]](`r na.omit(wk2$recording)[1]`) 

```{r wk2}
wk2 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

## `r format(wk3$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk3$Zoom)[1]`)[[Recording]](`r na.omit(wk3$recording)[1]`) 

```{r wk3}
wk3 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```
