---
title: "Computational Methods & Programming for Math Majors"
output:
  html_document:
    toc: no
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4); library(dplyr)
library(kableExtra); library(lubridate)

options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 

raw <- read_sheet("https://docs.google.com/spreadsheets/d/1MJG0lwuE9f03LXEtaH53j-uJGHwAsAO1ckP_jDAm0gY/edit#gid=1389752095") %>%
        mutate(dt = date(Date), 
               Name = paste(sprintf("[%s](%s)", Name, webpage), 
                            sprintf("[%s](mailto:%s)", Email, Email))) %>% 
        select(-Date, -`Confirmed?`, -Email, -webpage) %>%
        relocate(c(Time,Name), .before=1)
        

sep04 <- filter(raw, dt=="2020-09-04") %>% select(-dt) %>% arrange(Time)
sep11 <- filter(raw, dt=="2020-09-11") %>% select(-dt) %>% arrange(Time)
sep18 <- filter(raw, dt=="2020-09-18") %>% select(-dt) %>% arrange(Time)
sep25 <- filter(raw, dt=="2020-09-25") %>% select(-dt) %>% arrange(Time)
```
<br>


# Hosts: 

* Berit Givens, Professor & Chair Department of Mathematics & Statistics, Cal Poly Pomona. bngivens@cpp.edu
* Robin Donatello, Associate Professor of Statistics, Department of Mathematics & Statistics, Cal State Chico. rdonatello@csuchico.edu


<br>

# Friday September 4th [[Zoom Link]]()
```{r}
kable(sep04) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "10%") %>%
  column_spec(4, width = "20%") %>% 
  column_spec(5, width = "30%")
```

<br>

# Friday September 11th [[Zoom Link]]()
```{r}
kable(sep11) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "10%") %>%
  column_spec(4, width = "20%") %>% 
  column_spec(5, width = "30%")
```

<br>

# Friday September 18th [[Zoom Link]]()
```{r}
kable(sep18) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "10%") %>%
  column_spec(4, width = "20%") %>% 
  column_spec(5, width = "30%")
```

<br>

# Friday September 25th [[Zoom Link]]()
```{r}
kable(sep25) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "10%") %>%
  column_spec(4, width = "20%") %>% 
  column_spec(5, width = "30%")
```
