---
title: "November presentations"
output:
  html_document:
    toc: no
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4); library(dplyr)
library(kableExtra); library(lubridate)

options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 

raw <- read_sheet("https://docs.google.com/spreadsheets/d/1VjhdTRbQrnbgKvYvxaYUQRUDhzHItW0ITfUejQclBb4/edit#gid=1389752095") %>%
        mutate(dt = date(Date), 
               Name = paste(Name, sprintf("[%s](mailto:%s)", Email, Email)), 
               Affiliation = ifelse(!is.na(webpage), sprintf("[%s](%s)", Affiliation, webpage), Affiliation)) %>% 
        select(-Date, -`Confirmed?`, -Email, -webpage) %>%
        relocate(c(Time,Name), .before=1)


wk1 <- filter(raw, dt=="2021-11-05") %>% arrange(Time)
wk2 <- filter(raw, dt=="2021-11-12") %>% arrange(Time)
wk3 <- filter(raw, dt=="2021-11-19") %>% arrange(Time)

```

> The CSU Math Council Colloquia (MC$^2$) series provides CSU faculty in mathematics, statistics, and mathematics education with the opportunity to network and share best practices in any topics related to university level mathematics and statistics education.

----

Hosts: 

* **Claudia  Bertolone-Smith**, Assistant Professor of Education & Multiple Subjects Program Coordinator, California State University Chico (cmbertolone-smith@csuchico.edu)
* **Ferdie Rivera**, Professor, Department of Math & Statistics, San Jose State University (ferdinand.rivera@sjsu.edu)

This month there will be a discussion from 5:30-6pm following each presentation. 

----

## `r format(wk1$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk1$Zoom)[1]`) [[Recording]](`r na.omit(wk1$recording)[1]`)

### Theme: Access and Equity Perspectives and Practices in Mathematics Teaching and Learning

```{r, wk1}
wk1 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> <br> 

## `r format(wk2$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk2$Zoom)[1]`) [[Recording]](`r na.omit(wk2$recording)[1]`)

### Theme: Academic Literacy and Language in Mathematics from an Access and Equity Lens

```{r wk2}
wk2 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

## `r format(wk3$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk3$Zoom)[1]`)

### Theme: Culturally Relevant Mathematics Teaching from an Access and Equity Perspective

```{r wk3}
wk3 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```
