---
title: "January Presentations"
output:
  html_document:
    toc: no
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4); library(dplyr)
library(kableExtra); library(lubridate)

options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 

raw <- read_sheet("https://docs.google.com/spreadsheets/d/1MJG0lwuE9f03LXEtaH53j-uJGHwAsAO1ckP_jDAm0gY/edit#gid=1389752095", 
                  col_types="ccccccDcccc") %>%
        mutate(dt = date(Date), 
               Name = paste(Name, sprintf("[%s](mailto:%s)", Email, Email))) %>% 
        select(-Date, -`Confirmed?`, -Email, -webpage) %>%
        relocate(c(Time,Name), .before=1)


wk1 <- filter(raw, dt=="2021-01-08") %>% arrange(Time)
wk2 <- filter(raw, dt=="2021-01-15") %>% arrange(Time)
wk3 <- filter(raw, dt=="2021-01-22") %>% arrange(Time)
wk4 <- filter(raw, dt=="2021-01-29") %>% arrange(Time)

```

> The CSU Math Council Colloquia (MC$^2$) series provides CSU faculty in mathematics, statistics, and mathematics education with the opportunity to network and share best practices in any topics related to university level mathematics and statistics education.

----

# Peer Instruction and Tutoring

We hope to connect faculty and staff across the CSU who work on providing academic support services to students in mathematics and statistics courses.  In addition to the talks, we're interested in collecting some information on the structure of the tutoring and peer instruction on the various campuses.

Hosts: 

* **Bori Mazzag**, Professor & Chair of the Department of Mathematics & Computer Scieence, Humboldt State University. borbala.mazzag@humboldt.edu
* **Julie Glass**, Professor & Chair of the Department of Mathematics; CSU East Bay. julie.glass@csueastbay.edu


<br>

## `r format(wk1$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk1$Zoom)[1]`)  [[Recording]](`r na.omit(wk1$recording)[1]`) 
```{r, wk1}
wk1 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br>

## `r format(wk2$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk2$Zoom)[1]`)[[Recording]](`r na.omit(wk2$recording)[1]`) 

```{r wk2}
wk2 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```


<br>

## `r format(wk3$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk3$Zoom)[1]`)[[Recording]](`r na.omit(wk3$recording)[1]`) 

```{r wk3}
wk3 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br>

## `r format(wk4$dt[1], "%A, %B %d, %Y")` [[Zoom Link]](`r na.omit(wk4$Zoom)[1]`)[[Recording]](`r na.omit(wk4$recording)[1]`) 

```{r wk4}
wk4 %>% select(-Zoom, -recording, -dt) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

