---
title: "November presentations"
output:
  html_document:
    toc: no
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4); library(dplyr)
library(kableExtra); library(lubridate)

options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 

raw <- read_sheet("https://docs.google.com/spreadsheets/d/1MJG0lwuE9f03LXEtaH53j-uJGHwAsAO1ckP_jDAm0gY") %>%
        mutate(dt = date(Date), 
               Name = paste(Name, sprintf("[%s](mailto:%s)", Email, Email)), 
               Affiliation = ifelse(!is.na(webpage), sprintf("[%s](%s)", Affiliation, webpage), Affiliation)) %>% 
        select(-Date, -`Confirmed?`, -Email, -webpage, -recording) %>%
        relocate(c(Time,Name), .before=1)


nov06 <- filter(raw, dt=="2020-11-06") %>% select(-dt) %>% arrange(Time)
nov13 <- filter(raw, dt=="2020-11-13") %>% select(-dt) %>% arrange(Time)
nov20 <- filter(raw, dt=="2020-11-20") %>% select(-dt) %>% arrange(Time)

```

> The CSU Math Council Colloquia (MC$^2$) series provides CSU faculty in mathematics, statistics, and mathematics education with the opportunity to network and share best practices in any topics related to university level mathematics and statistics education.

----

# Issues in Mathematics Education for Preparing Teachers

Hosts: 

* **Rick Ford**, Professor, Department of Mathematics & Statistics, Cal State Chico. rford@csuchico.edu
* **Claudia M Bertolone-Smith **, Assistant Professor, School of Education, Cal State Chico. cmbertolone-smith@csuchico.edu 

----


## Friday November 6th [[Zoom Link]](`r na.omit(nov06$Zoom)[1]`)
```{r nov06}
nov06 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

## Friday November 13th [[Zoom Link]](`r na.omit(nov13$Zoom)[1]`)

[[Recorded Session]](https://fullerton.zoom.us/rec/share/OY0P1UU48XzLxz0Uc97nIGoJBXCfF0gy7uihk62dC5oCgSsdLXUAD-BVAr-POYs.TiIolCdcOqA0lb-2) Passcode: `=9CfTcK!`

```{r nov13}
nov13 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

## Friday November 20th [[Zoom Link]](`r na.omit(nov20$Zoom)[1]`) 
[[Recorded Session]](https://media.csuchico.edu/media/Issues+in+Math+Education+for+Preparing+Teachers+%28November+20th%2C+2020+Recording%29/1_rvf06nfs)
```{r nov20}
nov20 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

