---
title: "October Presentations"
output:
  html_document:
    toc: no
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4); library(dplyr)
library(kableExtra); library(lubridate)

options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 

raw <- read_sheet("https://docs.google.com/spreadsheets/d/1MJG0lwuE9f03LXEtaH53j-uJGHwAsAO1ckP_jDAm0gY/edit#gid=1389752095") %>%
        mutate(dt = date(Date), 
               Name = paste(Name, sprintf("[%s](mailto:%s)", Email, Email)), 
               Affiliation = sprintf("[%s](%s)", Affiliation, webpage)) %>% 
        select(-Date, -`Confirmed?`, -Email, -webpage) %>%
        relocate(c(Time,Name), .before=1)
oct02 <- filter(raw, dt=="2020-10-02") %>% select(-dt) %>% arrange(Time)
oct16 <- filter(raw, dt=="2020-10-16") %>% select(-dt) %>% arrange(Time)
oct23 <- filter(raw, dt=="2020-10-23") %>% select(-dt) %>% arrange(Time)
oct30 <- filter(raw, dt=="2020-10-30") %>% select(-dt) %>% arrange(Time)
```

> The CSU Math Council Colloquia (MC$^2$) series provides CSU faculty in mathematics, statistics, and mathematics education with the opportunity to network and share best practices in any topics related to university level mathematics and statistics education.

----

# Innovation in the Math Major Curriculum

#### Hosts: 

* Alfonso Agnew, Professor & Chair Department of Mathematics, CSU Fullerton,  aagnew@rullerton.edu

## Friday October 2nd [[Zoom Link]](`r na.omit(oct02$Zoom)[1]`)
```{r}
oct02 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

## Friday October 16th [[Zoom Link]](`r na.omit(oct16$Zoom)[1]`)
```{r}
oct16 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

<!---
## Friday October 23rd [[Zoom Link]](`r na.omit(oct23$Zoom)[1]`)
```{r}
oct23 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br> 

## Friday October 30th [[Zoom Link]](`r na.omit(oct30$Zoom)[1]`)
```{r}
oct30 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

--->



