---
title: "September Presentations"
output:
  html_document:
    toc: no
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4); library(dplyr)
library(kableExtra); library(lubridate)

options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 

raw <- read_sheet("https://docs.google.com/spreadsheets/d/1MJG0lwuE9f03LXEtaH53j-uJGHwAsAO1ckP_jDAm0gY/edit#gid=1389752095", 
                  col_types="ccccccDcccc") %>%
        mutate(dt = date(Date), 
               Name = paste(Name, sprintf("[%s](mailto:%s)", Email, Email)), 
               Affiliation = sprintf("[%s](%s)", Affiliation, webpage)) %>% 
        select(-Date, -`Confirmed?`, -Email, -webpage, -recording) %>%
        relocate(c(Time,Name), .before=1)


sep04 <- filter(raw, dt=="2020-09-04") %>% select(-dt) %>% arrange(Time)
sep11 <- filter(raw, dt=="2020-09-11") %>% select(-dt) %>% arrange(Time)
sep18 <- filter(raw, dt=="2020-09-18") %>% select(-dt) %>% arrange(Time)
sep25 <- filter(raw, dt=="2020-09-25") %>% select(-dt) %>% arrange(Time)

```

> The CSU Math Council Colloquia (MC$^2$) series provides CSU faculty in mathematics, statistics, and mathematics education with the opportunity to network and share best practices in any topics related to university level mathematics and statistics education.

----

# Computational Methods & Programming for Math & Stats Majors

For the September 2020 MC$^2$, faculty across the CSU share their insights and experiences with incorporating software and/or programming into courses for math and stats undergraduate majors.

Hosts: 

* **Berit Givens**, Professor & Chair Department of Mathematics & Statistics, Cal Poly Pomona. bngivens@cpp.edu
* **Robin Donatello**, Associate Professor of Statistics, Department of Mathematics & Statistics; Data Science Program Coordinator, Cal State Chico. rdonatello@csuchico.edu


<br>

## Friday September 4th [[Zoom Link]](`r na.omit(sep04$Zoom)[1]`)
```{r}
sep04 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br>

## Friday September 11th [[Zoom Link]](`r na.omit(sep11$Zoom)[1]`)
```{r}
sep11 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br>

## Friday September 18th [[Zoom Link]](`r na.omit(sep18$Zoom)[1]`)
```{r}
sep18 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

<br>

## Friday September 25th [[Zoom Link]](`r na.omit(sep25$Zoom)[1]`)
```{r}
sep25 %>% select(-Zoom) %>% kable() %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>%  
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "10%") %>%
  column_spec(3, width = "5%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```


